Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
add csv and visuals
Added regional csv and visuals to rmd

# Data
```{r}
Finaldata<- read.csv("FinalDataSet.csv")
```

@@

##Visualizations

>>>>

# Data
```{r}
Finaldata<- read.csv("FinalDataSet.csv")
```
```{r}
google<-read.csv("Google/googlefinal.csv")
```

@@

##Visualizations 
```{r}
google %>% 
  group_by(Region, Day) %>% 
  summarize(ChinaVirusSearch = median(ChinaVirusInterest)) %>% 
  ggplot(aes(x=Day, y=ChinaVirusSearch, color=Region))+
  geom_point()
```
